---
title: "ind_stimuli_wordFreq"
author: "Joemari Pulido"
date: "`r Sys.Date()`"
output: 
 md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



##Independent Study Intro The current study is Joemari Pulido's independent study advised by Dr. Joanna Morris. The current study aims to explore stereotype violations using the N400 erp component. The current script shows the code used to generate ngram frequencies of stimuli to be used in the current study.

Sean Carmody et al. created and maintain a package 'ngramr' which queries the Google Books Ngram Viewer. The Google Books Ngram Viewer corpus holds about 2 trillion words/phrases. The specific corpus the current study will be using is corpus 'en-2019' which contains data about word frequencies from 1950 up until 2019.

The following code block loads the package 'devtools'. Then, calls the function 'install_github' which enables one to install a repository directly from GitHub into RStudio. syntax is 'install_github("respositoryownner/repositoryname")'. Then, once the repository is loaded, load the 'ngramr' package into RStudio, which then allows you to enter a list of phrases to display a graph showing how often the phrases occurred in a given corpus.

#load necessary packages and install ngram package from seancarmody github repository

```{r load packages and install ngram from seancarmody github repository}
library(devtools)
install_github("seancarmody/ngramr")
library(ngramr)
library(ggplot2)
library(tidyverse)
library(SciViews)
```

syntax {r find average freq for and store in object} 
<- ngram(c(""), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
<- mean(\$Frequency) #calculate mean 
<- log() #calculate log

#r:sent The following code blocks will get the avg frequencies of each stimuli in race:sentences. First, I will limit the year's range to 2000 to 2019. Then, I qill get the average frequencty from 2000 to 2019 for each word or phrase and store it in a variable/object.Then, I will calculate the natural log of the average frequencies of each word. Then, I will create a table/tibble of all the variables containing the natural log of average frequencies for each word. After, I will plot this table in a graph.

#janitor:rsent

```{r find average freq for janitor and store in object }
Janitor <- ngram("Janitor", corpus = "en-2019", year_start = 2000, year_end = 2019,smoothing = 3, case_ins = FALSE)
Janitor <- mean(Janitor$Frequency) #calculate mean
Janitor <-log(Janitor) #calculate log
```

#engineer:rsent

```{r find average freq for engineer and store in object Engineer}
Engineer <- ngram(c("Engineer"), corpus = "en-2019", year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
Engineer <- mean(Engineer$Frequency) #calculate mean
Engineer<- log(Engineer) #calculate log
```

#basketball:rsent

```{r find average freq for Basketballplayer and store in object Basketball}
Basketball <- ngram(c("Basketball"), corpus = "en-2019", year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
Basketball <- mean(Basketball$Frequency) #calculate mean
Basketball <- log(Basketball) #calculate log
```

#yoga:rsent

```{r find average freq for yoga instructor and store in object Yoga}
Yoga<- ngram(c("Yoga"), corpus = "en-2019", year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
Yoga <- mean(Yoga$Frequency) #calculate mean 
Yoga <- log(Yoga) #calculate log
```

#business:rsent

```{r find average freq for Business executive and store in object Business }
Business<- ngram(c("Business"), corpus = "en-2019", year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
Business <- mean(Business$Frequency) #calculate mean
Business <- log(Business) #calculate log
```

#mcdonalds:rsent

```{r find average freq for McDonalds worker and store in object  Mcdonalds}
Mcdo<- ngram(c("McDonalds+worker"), corpus = "en-2019", year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
Mcdo<- mean(Mcdo$Frequency) #calculate mean 
Mcdo <- log(Mcdo) #calculate log
```

#creative:rsent

```{r find average freq for Creative Writing Major and store in object  Creative }
Creative<- ngram(c("Creative"), corpus = "en-2019", year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
Creative<- mean(Creative$Frequency) #calculate mean
Creative <- log(Creative) #calculate log
```

#nailtech:rsent

```{r find average freq for nail tech and store in object  nailtech }
nailtech <- ngram(c("Nail+tech"), corpus = "en-2019",year_start = 2000,year_end = 2019, smoothing = 3, case_ins = FALSE)
nailtech <- mean(nailtech$Frequency) #calculate mean 
nailtech<- log(nailtech) #calculate log
```

#cardiologist:rsent

```{r find average freq for cardiologist and store in object  cardiologist}
cardiologist<- ngram(c("cardiologist"), corpus = "en-2019",year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
cardiologist<- mean(cardiologist$Frequency) #calculate mean 
cardiologist<- log(cardiologist) #calculate log
```

#rapper:rsent

```{r find average freq for rapper and store in object rapper }
rapper<- ngram(c("rapper"),corpus = "en-2019",year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
rapper<- mean(rapper$Frequency) #calculate mean 
rapper<- log(rapper) #calculate log
```

#cafeteria:rsent

```{r find average freq for cafeteria and store in object cafeteria }
cafeteria<- ngram(c("cafeteria+worker"),corpus = "en-2019", year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
cafeteria<- mean(cafeteria$Frequency) #calculate mean 
cafeteria<- log(cafeteria) #calculate log
```

#psycholgist:rsent

```{r find average freq for psychologist and store in object psychologist }
psychologist<- ngram(c("psychologist"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
psychologist<- mean(psychologist$Frequency) #calculate mean 
psychologist<- log(psychologist) #calculate log
```

#hiphop:rsent

```{r find average freq for hiphopdancerand store in object  hiphop}
hiphop<- ngram(c("hiphop+dancer"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
hiphop<- mean(hiphop$Frequency) #calculate mean 
hiphop<- log(hiphop) #calculate log
```

#cs:rsent

```{r find average freq for computer scientist and store in object  cs}
cs<- ngram(c("computer+scientist"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
cs<- mean(cs$Frequency) #calculate mean 
cs<- log(cs) #calculate log
```

#counselor:rsent

```{r find average freq for counselor and store in object counselor }
counselor<- ngram(c("counselor"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
counselor<- mean(counselor$Frequency) #calculate mean 
counselor<- log(counselor) #calculate log
```

#physical therapist:rsent

```{r find average freq for physical therapist and store in object pt }
pt<- ngram(c("physical+therapist"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
pt<- mean(pt$Frequency) #calculate mean 
pt<- log(pt) #calculate log
```

#unemployed:rsent

```{r find average freq for unemployed and store in object unemployed}
unemployed<- ngram(c("unemployed"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
unemployed<- mean(unemployed$Frequency) #calculate mean 
unemployed<- log(unemployed) #calculate log
```

#Burgerking:rsent

```{r find average freq for burgerking worker and store in object burgerking }
burgerKing<- ngram(c("burgerking+worker"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
burgerKing<- mean(burgerKing$Frequency) #calculate mean 
burgerKing<- log(burgerKing) #calculate log
```

#EnglishProfessor:rsent

```{r find average freq for English Professor and store in object englishProf }
englishProf<- ngram(c("English+Professor"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
englishProf<- mean(englishProf$Frequency) #calculate mean 
englishProf<- log(englishProf) #calculate log
```

#AdministrativeAssistant:rsent

```{r find average freq for administrative assistant and store in object  adminassi}
adminassi<- ngram(c("administrative+assistant"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
adminassi<- mean(adminassi$Frequency) #calculate mean 
adminassi<- log(adminassi) #calculate log
```

#MathematichsProfessor:rsent

```{r find average freq for mathematics professor and store in object mathProf }
mathProf<- ngram(c("Mathematics+Professor"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
mathProf<- mean(mathProf$Frequency) #calculate mean 
mathProf<- log(mathProf) #calculate log
```

#speechpathologist:rsent

```{r find average freq for speech pathologist and store in object speech  }
speechpath<- ngram(c("speech+pathologist"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
speechpath<- mean(speechpath$Frequency) #calculate mean 
speechpath<- log(speechpath) #calculate log
```

#realestate:rsent

```{r find average freq for realestate agent and store in object realestate }
realestate<- ngram(c("real+estate+agent"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
realestate<- mean(realestate$Frequency) #calculate mean 
realestate<- log(realestate) #calculate log
```

#highschooldropout:rsent

```{r find average freq for high school drop out and store in object highdrop }
highdrop<- ngram(c("highschool+dropout"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
highdrop<- mean(highdrop$Frequency) #calculate mean 
highdrop<- log(highdrop) #calculate log
```

#PsychologyProfessor:rsent

```{r find average freq for psychology professor and store in object psyProf }
psyProf<- ngram(c("psychology+Professor"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
psyProf<- mean(psyProf$Frequency) #calculate mean 
psyProf<- log(psyProf) #calculate log
```

#BusDriver:rsent

```{r find average freq for bus driver and store in object busDriver}
busDriver<- ngram(c("bus+driver"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
busDriver<- mean(busDriver$Frequency) #calculate mean 
busDriver<- log(busDriver) #calculate log
```

#Techconsultant:rsent

```{r find average freq for tech consultant and store in object techconsul}
techConsul<- ngram(c("tech+consultant"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
techConsul<- mean(techConsul$Frequency) #calculate mean 
techConsul<- log(techConsul) #calculate log
```

#pilatesinstructor:rsent

```{r find average freq forpilates instructor and store in object pilates}
pilates<- ngram(c("pilates+instructor"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
pilates<- mean(pilates$Frequency) #calculate mean 
pilates<- log(pilates) #calculate log
```

#poet:rsent

```{r find average freq for poet and store in object poet}
poet<- ngram(c("poet"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
poet<- mean(poet$Frequency) #calculate mean 
poet<- log(poet) #calculate log
```

#congressman:rsent

```{r find average freq for congressman and store in object congressm }
congressm<- ngram(c("congressman"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
congressm<- mean(congressm$Frequency) #calculate mean 
congressm<- log(congressm) #calculate log
```

#trainconductor:rsent

```{r find average freq for trainconductor and store in object traincond}
traincond<- ngram(c("train+conductor"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
traincond<- mean(traincond$Frequency) #calculate mean 
traincond<- log(traincond) #calculate log
```

#socialworker:rsent

```{r find average freq for social worker and store in object socialwork}
socialwork<- ngram(c("social+worker"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
socialwork<- mean(socialwork$Frequency) #calculate mean 
socialwork<- log(socialwork) #calculate log
```

#collegedropout:rsent

```{r find average freq for college drop out and store in object collegedrop}
collegedrop<- ngram(c("Dropout"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
collegedrop<- mean(collegedrop$Frequency) #calculate mean 
collegedrop<- log(collegedrop) #calculate log
```

#civilengineer:rsent

```{r find average freq for civil engineer and store in object civileng}
civileng<- ngram(c("civil+engineer"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
civileng<- mean(civileng$Frequency) #calculate mean 
civileng<- log(civileng) #calculate log
```

#philosophyprofessor:rsent

```{r find average freq for philosophy professor and store in object phlProf}
phlProf<- ngram(c("philosophy+professor"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
phlProf<- mean(phlProf$Frequency) #calculate mean 
phlProf<- log(phlProf) #calculate log
```

#maintenanceworker:rsent

```{r find average freq for maintenance worker and store in object mainWorker}
mainWorker<- ngram(c("maintenance+worker"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
mainWorker<- mean(mainWorker$Frequency) #calculate mean 
mainWorker<- log(mainWorker) #calculate log
```

#housekeeper:rsent

```{r find average freq for housekeeper and store in objecthousekeeper}
housekeeper<- ngram(c("housekeeper"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
housekeeper<- mean(housekeeper$Frequency) #calculate mean 
housekeeper<- log(housekeeper) #calculate log
```

#secretary:rsent

```{r find average freq for secretary and store in object secretary}
secretary<- ngram(c("secretary"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
secretary<- mean(secretary$Frequency) #calculate mean 
secretary<- log(secretary) #calculate log
```

#criminal:rsent

```{r find average freq for criminal and store in object criminal}
criminal<- ngram(c("criminal"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
criminal<- mean(criminal$Frequency) #calculate mean 
criminal<- log(criminal) #calculate log
```

#lawyer:rsent

```{r find average freq for lawyer and store in object lawyer}
lawyer<- ngram(c("lawyer"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
lawyer<- mean(lawyer$Frequency) #calculate mean 
lawyer<- log(lawyer) #calculate log
```

#lawclerk:rsent

```{r find average freq for lawclerk and store in object lawClerk}
lawClerk<- ngram(c("law+clerk"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
lawClerk<- mean(lawClerk$Frequency) #calculate mean 
lawClerk<- log(lawClerk) #calculate log
```

#AccountingProfessor:rsent

```{r find average freq for accounting professor and store in object accProf}
accProf<- ngram(c("accounting+Professor"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
accProf<- mean(accProf$Frequency) #calculate mean 
accProf<- log(accProf) #calculate log
```

#jazzmusician:rsent

```{r find average freq for jazz musician and store in object jazzMus}
jazzMus<- ngram(c("jazz+musician"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
jazzMus<- mean(jazzMus$Frequency) #calculate mean 
jazzMus<- log(jazzMus) #calculate log
```

#gender:sent The following code blocks will get the avg frequencies of each stimuli in gender:sentences. First, I will limit the year's range to 2000 to 2019. Then, I qill get the average frequencty from 2000 to 2019 for each word or phrase and store it in a variable/object.Then, I will calculate the natural log of the average frequencies of each word. Then, I will create a table/tibble of all the variables containing the natural log of average frequencies for each word. After, I will plot this table in a graph.

#Hairdresser:gsent

```{r find average freq for hairdresser and store in object hairdresser}
hairdresser<- ngram(c("hairdresser"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
hairdresser<- mean(hairdresser$Frequency) #calculate mean 
hairdresser<- log(hairdresser) #calculate log
```

#CEO:gsent

```{r find average freq for CEO and store in object CEO }
CEO<- ngram(c("CEO"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
CEO<- mean(CEO$Frequency) #calculate mean 
CEO<- log(CEO) #calculate log
```

#Housecleaner:gsent

```{r find average freq for housecleanerand store in object housecleaner}
housecleaner<- ngram(c("housecleaner"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
housecleaner<- mean(housecleaner$Frequency) #calculate mean 
housecleaner<- log(housecleaner) #calculate log
```

#Data analyst:gsent

```{r find average freq for data analyst and store in object }
dataanalyst<- ngram(c("data+analyst"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
dataanalyst<- mean(dataanalyst$Frequency) #calculate mean 
dataanalyst<- log(dataanalyst) #calculate log
```

#Elementaryteacher:gsent

```{r find average freq for elementary teacher and store in object elemteacher}
elemteacher<- ngram(c("elementary+teacher"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
elemteacher<- mean(elemteacher$Frequency) #calculate mean 
elemteacher<- log(elemteacher) #calculate log
```

#President:gsent

```{r find average freq for president and store in object president}
president<- ngram(c("president"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
president<- mean(president$Frequency) #calculate mean 
president<- log(president) #calculate log
```

#nursing:gsent

```{r find average freq for nurse and store in object nurse}
nurse<- ngram(c("nurse"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
nurse<- mean(nurse$Frequency) #calculate mean 
nurse<- log(nurse) #calculate log
```

#Business:gsent

```{r find average freq for business executive  and store in object executive}
executive<- ngram(c("business+executive"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
executive<- mean(executive$Frequency) #calculate mean 
executive<- log(executive) #calculate log
```

#Fashion:gsent

```{r find average freq for fashion majorand store in object fashion }
fashion<- ngram(c("fashion+major"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
fashion<- mean(fashion$Frequency) #calculate mean 
fashion<- log(fashion) #calculate log
```

#Neurologist:gsent

```{r find average freq for neurologist and store in object neurologist}
neurologist<- ngram(c("Neurologist"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
neurologist<- mean(neurologist$Frequency) #calculate mean 
neurologist<- log(neurologist) #calculate log
```

#preschool:gsent

```{r find average freq for preschool teacher and store in object preschool teacher}
preTeacher<- ngram(c("preschool+teacher"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
preTeacher<- mean(preTeacher$Frequency) #calculate mean 
preTeacher<- log(preTeacher) #calculate log
```

#Chemical engineer:gsent

```{r find average freq for chemical engineer and store in object chemEng }
chemEng<- ngram(c("chemical+engineer"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
chemEng<- mean(chemEng$Frequency) #calculate mean 
chemEng<- log(chemEng) #calculate log
```

#makeupartist:gsent

```{r find average freq for makeupartist and store in object mua }
mua<- ngram(c("makeup+artist"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
mua<- mean(mua$Frequency) #calculate mean 
mua<- log(mua) #calculate log
```


#Babysitter:gsent

```{r find average freq for babysitter and store in object babysitter }
babysitter<- ngram(c("babysitter"), year_start = 2000, year_end = 2019, smoothing = 3, case_ins = FALSE)
babysitter<- mean(babysitter$Frequency) #calculate mean 
babysitter<- log(babysitter) #calculate log
```

#weightlifter:gsent

```{r find average freq for weightlifter and store in object weightlifter}
weightlifter<- ngram(c("weightlifter"), year_start = 2000, corpus = "en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE)
weightlifter<- mean(weightlifter$Frequency) #calculate mean 
weightlifter<- log(weightlifter) #calculate log
```

#midwife:gsent

```{r find average freq for midwife and store in object midwife}
midwife<- ngram(c("midwife"), year_start = 2000, corpus = "en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE)
midwife<- mean(midwife$Frequency) #calculate mean 
midwife<- log(midwife) #calculate log
```

#Neurosurgeon:gsent

```{r find average freq for neurosurgeon and store in object neurosurgeon }
neurosurgeon<- ngram(c("neurosurgeon"), year_start = 2000, corpus = "en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE)
neurosurgeon<- mean(neurosurgeon$Frequency) #calculate mean 
neurosurgeon<- log(neurosurgeon) #calculate log
```

#ArmyGeneral:gsent

```{r find average freq for armygeneral and store in object armygeneral }
armygeneral<- ngram(c("army+general"), year_start = 2000, corpus = "en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE)
armygeneral<- mean(armygeneral$Frequency) #calculate mean 
armygeneral<- log(armygeneral) #calculate log
```

#Industrial:gsent

```{r find average freq for industrial engineer and store in object industrialEng}
industrialEng<- ngram(c("Industrial+Engineer"), year_start = 2000, corpus = "en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE)
industrialEng<- mean(industrialEng$Frequency) #calculate mean 
industrialEng<- log(industrialEng) #calculate log
```

#Librarian:gsent

```{r find average freq forlibrarian and store in object librarian}
librarian<- ngram(c("librarian"), year_start = 2000, corpus = "en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE)
librarian<- mean(librarian$Frequency) #calculate mean 
librarian<- log(librarian) #calculate log
```

#Captain:gsent

```{r find average freq for airforcecaptain and store in object aircaptain}
aircaptain<- ngram(c("Airforce+Captain"), year_start = 2000, corpus = "en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE)
aircaptain<- mean(aircaptain$Frequency) #calculate mean 
aircaptain<- log(aircaptain) #calculate log
```

#Carpenter:gsent

```{r find average freq for carpenter and store in object carpenter}
carpenter<- ngram(c("Carpenter"), year_start = 2000, corpus = "en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE)
carpenter<- mean(carpenter$Frequency) #calculate mean 
carpenter<- log(carpenter) #calculate log
```

#Teaching:gsent
```{r find average freq for teaching assistant and store in object teachingAssistant} 
teachingAssistant<- ngram(c("Teaching+Assistant"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
teachingAssistant<- mean(teachingAssistant$Frequency) #calculate mean 
teachingAssistant<- log(teachingAssistant) #calculate log
```

#Therapist:gsent
```{r find average freq for Therapist and store in object therapist} 
therapist<- ngram(c("Therapist"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
therapist<- mean(therapist$Frequency) #calculate mean 
therapist<- log(therapist) #calculate log
```

#Firefighter:gsent
```{r find average freq for firefighter and store in object firefighter} 
firefighter<- ngram(c("Firefighter"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
firefighter<- mean(firefighter$Frequency) #calculate mean 
firefighter<- log(firefighter) #calculate log
```

#Child:gsent
```{r find average freq for child psychologist and store in object childPsychologist} 
childPsychologist<- ngram(c("Child+Psychologist"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
childPsychologist<- mean(childPsychologist$Frequency) #calculate mean 
childPsychologist<- log(childPsychologist) #calculate log
```

#Architect:gsent
```{r find average freq for architect and store in object architect} 
architect<- ngram(c("architect"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
architect<- mean(architect$Frequency) #calculate mean 
architect<- log(architect) #calculate log
```


#Flight:gsent
```{r find average freq for flight attendant and store in object flight attendant} 
flightAttendant<- ngram(c("flight+Attendant"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
flightAttendant<- mean(flightAttendant$Frequency) #calculate mean 
flightAttendant<- log(flightAttendant) #calculate log
```


#School:gsent
```{r find average freq for school counselor and store in object schoolCounselor} 
schoolCounselor<- ngram(c("School+Counselor"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
schoolCounselor<- mean(schoolCounselor$Frequency) #calculate mean 
schoolCounselor<- log(schoolCounselor) #calculate log
```

#Landscaper:gsent
```{r find average freq for landscaper and store in object landscaper} 
landscaper<- ngram(c("landscaper"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
landscaper<- mean(landscaper$Frequency) #calculate mean 
landscaper<- log(landscaper) #calculate log
```

#Sewing:gsent
```{r find average freq for factoryWorker and store in object factoryWorker} 
factoryWorker<- ngram(c("Factory+Worker"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
factoryWorker<- mean(factoryWorker$Frequency) #calculate mean 
factoryWorker<- log(factoryWorker) #calculate log
```

#Electrician:gsent
```{r find average freq for electrician and store in object electrician } 
electrician<- ngram(c("Electrician"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
electrician<- mean(electrician$Frequency) #calculate mean 
electrician<- log(electrician) #calculate log
```

#Florist:gsent
```{r find average freq for florist and store in object florist} 
florist <- ngram(c("florist"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
florist<- mean(florist$Frequency) #calculate mean 
florist<- log(florist) #calculate log
```

#Construction:gsent
```{r find average freq for construction Worker and store in object constructionWorker}
constructionWorker<- ngram(c("Construction+Worker"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
constructionWorker<- mean(constructionWorker$Frequency) #calculate mean 
constructionWorker<- log(constructionWorker) #calculate log
```

#Office:gsent
```{r find average freq for office Clerk and store in object officeClerk} 
officeClerk<- ngram(c("Office+clerk"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
officeClerk<- mean(officeClerk$Frequency) #calculate mean 
officeClerk<- log(officeClerk) #calculate log
```

#Wall:gsent
```{r find average freq for wall tiler and store in object wallTiler} 
wallTiler<- ngram(c("Wall+Tiler"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
wallTiler<- mean(wallTiler$Frequency) #calculate mean 
wallTiler<- log(wallTiler) #calculate log
```

#Forklift:gsent
```{r find average freq for forklift driver and store in object forkliftDriver} 
forkliftDriver<- ngram(c("Forklift+Driver"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
forkliftDriver<- mean(forkliftDriver$Frequency) #calculate mean 
forkliftDriver<- log(forkliftDriver) #calculate log
```

##Part 2---------

#Engineer
```{r find average freq Engineer for and store in object engineer} 
engineer<- ngram(c("Engineer"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
engineer<- mean(engineer$Frequency) #calculate mean 
engineer<- log(engineer) #calculate log
```

#Basketball
```{r find average freq for Basketball and store in object basketball} 
basketball<- ngram(c("basketball"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
basketball<- mean(basketball$Frequency) #calculate mean 
basketball<- log(basketball) #calculate log
```

#CEO
```{r find average freq for CEO and store in object ceo} 
ceo<- ngram(c("CEO"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
ceo<- mean(ceo$Frequency) #calculate mean 
ceo<- log(ceo) #calculate log
```

#Criminal
```{r find average freq for Criminal and store in object criminal} 
criminal <- ngram(c("Criminal"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
criminal<- mean(criminal$Frequency) #calculate mean 
criminal<- log(criminal) #calculate log
```

#Achievement
```{r find average freq for achievement and store in object achievement} 
achievement<- ngram(c("Achievement"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
achievement<- mean(achievement$Frequency) #calculate mean 
achievement<- log(achievement) #calculate log
```

#Homeless
```{r find average freq for homeless and store in object homeless} 
homeless<- ngram(c("Homeless"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
homeless<- mean(homeless$Frequency) #calculate mean 
homeless<- log(homeless) #calculate log
```

#Doctor
```{r find average freq for Doctor and store in object doctor} 
doctor<- ngram(c("Doctor"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
doctor<- mean(doctor$Frequency) #calculate mean 
doctor<- log(doctor) #calculate log
```

#Janitor
```{r find average freq janitor for and store in object janitor} 
janitor<- ngram(c("Janitor"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
janitor<- mean(janitor$Frequency) #calculate mean 
janitor<- log(janitor) #calculate log
```

#Cop
```{r find average freq for cop and store in object cop} 
cop<- ngram(c("Cop"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
cop<- mean(cop$Frequency) #calculate mean 
cop<- log(cop) #calculate log
```

#Thief
```{r find average freq for thief and store in object thief} 
thief<- ngram(c("Thief"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
thief<- mean(thief$Frequency) #calculate mean 
thief<- log(thief) #calculate log
```

#Racist
```{r find average freq for racist and store in object racist} 
racist<- ngram(c("Racist"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
racist<- mean(racist$Frequency) #calculate mean 
racist<- log(racist) #calculate log
```

#Aggresive
```{r find average freq for aggressive and store in object aggressive} 
aggressive<- ngram(c("Aggressive"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
aggressive<- mean(aggressive$Frequency) #calculate mean 
aggressive<- log(aggressive) #calculate log
```

#Boss
```{r find average freq for boss and store in object boss} 
boss<- ngram(c("Boss"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
boss<- mean(boss$Frequency) #calculate mean 
boss<- log(boss) #calculate log
```

#Poverty
```{r find average freq for poverty and store in object poverty} 
poverty<- ngram(c("Poverty"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
poverty<- mean(poverty$Frequency) #calculate mean 
poverty<- log(poverty) #calculate log
```

#Redneck
```{r find average freq for redneck and store in object redneck} 
redneck<- ngram(c("Red+neck"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
redneck<- mean(redneck$Frequency) #calculate mean 
redneck<- log(redneck) #calculate log
```

#Diabetes
```{r find average freq for diabetes and store in object diabetes} 
diabetes<- ngram(c("Diabetes"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
diabetes<- mean(diabetes$Frequency) #calculate mean 
diabetes<- log(diabetes) #calculate log
```

#Professor
```{r find average freq for professor and store in object professor} 
professor<- ngram(c("Professor"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
professor<- mean(professor$Frequency) #calculate mean 
professor<- log(professor) #calculate log
```

#Cocaine
```{r find average freq for cocaine and store in object cocaine} 
cocaine<- ngram(c("Cocaine"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
cocaine<- mean(cocaine$Frequency) #calculate mean 
cocaine<- log(cocaine) #calculate log
```

#Unseasoned 
```{r find average freq for unseasoned and store in object unseasoned} 
unseasoned<- ngram(c("Unseasoned"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
unseasoned<- mean(unseasoned$Frequency) #calculate mean 
unseasoned<- log(unseasoned) #calculate log
```

#Spices
```{r find average freq for spices and store in object spices} 
spices<- ngram(c("Spices"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
spices<- mean(spices$Frequency) #calculate mean 
spices<- log(spices) #calculate log
```

#Congressman
```{r find average freq for Congressman and store in object congressman} 
congressman<- ngram(c("Congressman"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
congressman<- mean(congressman$Frequency) #calculate mean 
congressman<- log(congressman) #calculate log
```

#rnb
```{r find average freq for RNB and store in object rnb} 
rnb<- ngram(c("RNB"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
rnb<- mean(rnb$Frequency) #calculate mean 
rnb<- log(rnb) #calculate log
```

#Captain
```{r find average freq for captain and store in object captain} 
captain<- ngram(c("Captain"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
captain<- mean(captain$Frequency) #calculate mean 
captain<- log(captain) #calculate log
```

#Gang
```{r find average freq for gang and store in object gang} 
gang<- ngram(c("Gang"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
gang<- mean(gang$Frequency) #calculate mean 
gang<- log(gang) #calculate log
```

#Scientist
```{r find average freq for scientist and store in object scientist} 
scientist<- ngram(c("scientist"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
scientist<- mean(scientist$Frequency) #calculate mean 
scientist<- log(scientist) #calculate log
```

#Lazy
```{r find average freq for lazy and store in object lazy} 
lazy<- ngram(c("Lazy"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
lazy<- mean(lazy$Frequency) #calculate mean 
lazy<- log(lazy) #calculate log
```

#General
```{r find average freq for General and store in object general} 
general<- ngram(c("General_NOUN"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
general<- mean(general$Frequency) #calculate mean 
general<- log(general) #calculate log
```

#Villain
```{r find average freq for villain and store in object villain} 
villain<- ngram(c("villain"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
villain<- mean(villain$Frequency) #calculate mean 
villain<- log(villain) #calculate log
```

#Industrious
```{r find average freq for industrious and store in object industrious} 
industrious<- ngram(c("Industrious"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
industrious<- mean(industrious$Frequency) #calculate mean 
industrious<- log(industrious) #calculate log
```

#Ignorant
```{r find average freq for ignorant and store in object ignorant} 
ignorant<- ngram(c("Ignorant"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
ignorant<- mean(ignorant$Frequency) #calculate mean 
ignorant<- log(ignorant) #calculate log
```

#Ambitious
```{r find average freq for ambitious and store in object ambitious} 
ambitious<- ngram(c("Ambitious"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
ambitious<- mean(ambitious$Frequency) #calculate mean 
ambitious<- log(ambitious) #calculate log
```

#Musical
```{r find average freq for nusical and store in object musical} 
musical<- ngram(c("Musical"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
musical<- mean(musical$Frequency) #calculate mean 
musical<- log(musical) #calculate log
```

#Progressive
```{r find average freq for progressive and store in object progressive} 
progressive<- ngram(c("Progressive"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
progressive<- mean(progressive$Frequency) #calculate mean 
progressive<- log(progressive) #calculate log
```

#Dancer
```{r find average freq for dancer and store in object dancer} 
dancer<- ngram(c("Dancer"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
dancer<- mean(dancer$Frequency) #calculate mean 
dancer<- log(dancer) #calculate log
```

#Loud
```{r find average freq for loud and store in object loud} 
loud<- ngram(c("Loud"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
loud <- mean(loud$Frequency) #calculate mean 
loud<- log(loud) #calculate log
```

#Hip Hop
```{r find average freq for hip hop and store in object hiphop} 
hiphop<- ngram(c("Hip+hop"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
hiphop<- mean(hiphop$Frequency) #calculate mean 
hiphop<- log(hiphop) #calculate log
```

#Authority
```{r find average freq for authority and store in object authority} 
authority<- ngram(c("Authority"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
authority<- mean(authority$Frequency) #calculate mean 
authority<- log(authority) #calculate log
```

#Rap
```{r find average freq for rap and store in object rap } 
rap<- ngram(c("Rap"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
rap<- mean(rap$Frequency) #calculate mean 
rap<- log(rap) #calculate log
```

#Privilege
```{r find average freq for privilege and store in object privilege} 
privilege<- ngram(c("Privilege"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
privilege<- mean(privilege$Frequency) #calculate mean 
privilege<- log(privilege) #calculate log
```

#Violence
```{r find average freq for violenceand store in object violence} 
violence<- ngram(c("Violence"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
violence<- mean(violence$Frequency) #calculate mean 
violence<- log(violence) #calculate log
```

#Entitlement
```{r find average freq for entitlement and store in object entitlement} 
entitlement<- ngram(c("entitlement"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
entitlement<- mean(entitlement$Frequency) #calculate mean 
entitlement<- log(entitlement) #calculate log
```

#Healthcare
```{r find average freq for healthcare and store in object healthcare} 
healthcare<- ngram(c("healthcare"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
healthcare<- mean(healthcare$Frequency) #calculate mean 
healthcare<- log(healthcare) #calculate log
```

#Researcher
```{r find average freq for researcher and store in object researcher} 
researcher<- ngram(c("researcher"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
researcher<- mean(researcher$Frequency) #calculate mean 
researcher<- log(researcher) #calculate log
```

#Teen Mom
```{r find average freq for teenmom and store in objectteenmom} 
teenmom<- ngram(c("teen+mom"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
teenmom<- mean(teenmom$Frequency) #calculate mean 
teenmom<- log(teenmom) #calculate log
```

#Purity
```{r find average freq for purity and store in object purity} 
purity<- ngram(c("purity"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
purity<- mean(purity$Frequency) #calculate mean 
purity<- log(purity) #calculate log
```

#Beggar
```{r find average freq for beggar and store in object beggar} 
beggar<- ngram(c("Beggar"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
beggar<- mean(beggar$Frequency) #calculate mean 
beggar<- log(beggar) #calculate log
```

#Colonizer
```{r find average freq for colonizer and store in object colonizer} 
colonizer<- ngram(c("Colonizer"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
colonizer<- mean(colonizer$Frequency) #calculate mean 
colonizer<- log(colonizer) #calculate log
```

#Struggling
```{r find average freq for struggling and store in object struggling} 
struggling<- ngram(c("Struggling"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
struggling<- mean(struggling$Frequency) #calculate mean 
struggling<- log(struggling) #calculate log
```

#Nurturing
```{r find average freq for nurturing and store in object nurturing} 
nurturing<- ngram(c("nurturing"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
nurturing<- mean(nurturing$Frequency) #calculate mean 
nurturing<- log(nurturing) #calculate log
```

#Angry
```{r find average freq for angry and store in object angry} 
angry <- ngram(c("Angry"), year_start = 2000, corpus ="en-2019", year_end = 2019, smoothing = 3, case_ins = FALSE) 
angry<- mean(angry$Frequency) #calculate mean 
angry<- log(angry) #calculate log
```
#dataframe 
Create a data frame / tibble with each word and their frequency

```{r create table with objects }
freq2 <- c(achievement, aggressive, ambitious, angry, authority, basketball, beggar, boss, captain, ceo, cocaine, colonizer, congressman, cop, criminal, dancer, diabetes, doctor, engineer, entitlement, gang, general, healthcare, hiphop, homeless, ignorant, industrious, janitor, lazy, loud, musical, nurturing, poverty, privilege, professor, progressive, purity, racist, rap, redneck, researcher, rnb, scientist, spices, struggling, teenmom, thief, unseasoned, villain, violence)

names(freq2)[1] <- "achievement"
names(freq2)[2] <- "aggressive"
names(freq2)[3] <- "ambitious"
names(freq2)[4] <- "angry"
names(freq2)[5] <- "authority"
names(freq2)[6] <- "basketball"
names(freq2)[7] <- "beggar"
names(freq2)[8] <- "boss"
names(freq2)[9] <- "captain"
names(freq2)[10] <- "ceo"
names(freq2)[11] <- "cocaine"
names(freq2)[12] <- "colonizer"
names(freq2)[13] <- "congressman"
names(freq2)[14] <- "cop"
names(freq2)[15] <- "criminal"
names(freq2)[16] <- "dancer"
names(freq2)[17] <- "diabetes"
names(freq2)[18] <- "doctor"
names(freq2)[19] <- "engineer"
names(freq2)[20] <- "entitlement"
names(freq2)[21] <- "gang"
names(freq2)[22] <- "general"
names(freq2)[23] <- "healthcare"
names(freq2)[24] <- "hiphop"
names(freq2)[25] <- "homeless"
names(freq2)[26] <- "ignorant"
names(freq2)[27] <- "industrious"
names(freq2)[28] <- "janitor"
names(freq2)[29] <- "lazy"
names(freq2)[30] <- "loud"
names(freq2)[31] <- "musical"
names(freq2)[32] <- "nurturing"
names(freq2)[33] <- "poverty"
names(freq2)[34] <- "privilege"
names(freq2)[35] <- "professor"
names(freq2)[36] <- "progressive"
names(freq2)[37] <- "purity"
names(freq2)[38] <- "racist"
names(freq2)[39] <- "rap"
names(freq2)[40] <- "redneck"
names(freq2)[41] <- "researcher"
names(freq2)[42] <- "rnb"
names(freq2)[43] <- "scientist"
names(freq2)[44] <- "spices"
names(freq2)[45] <- "struggling"
names(freq2)[46] <- "teenmom"
names(freq2)[47] <- "thief "
names(freq2)[48] <- "unseasoned"
names(freq2)[49] <- "villain"
names(freq2)[50] <- "violence"
```

```{r put word with log(avg freq) iiin a data frame}
freqdataframe02<- as.data.frame(freq2)
colnames(freqdataframe02)
names(freqdataframe02)[names(freqdataframe02) == "freq2"] <- "freq"
```

```{r }
#create vector with the objects created 
freq <- c(accProf, adminassi, aircaptain, architect, armygeneral,babysitter, Basketball, burgerKing, busDriver, Business, cafeteria,cardiologist,carpenter,CEO,chemEng,childPsychologist, civileng, collegedrop, congressm, constructionWorker, counselor, Creative, criminal, cs, dataanalyst, electrician, elemteacher, Engineer, englishProf, executive, factoryWorker, fashion, firefighter, flightAttendant, florist, forkliftDriver, hairdresser, highdrop, hiphop, housecleaner, industrialEng, Janitor, jazzMus, landscaper, lawClerk, lawyer, librarian, mainWorker, mathProf, Mcdo, midwife, mua, nailtech, neurologist, neurosurgeon, nurse, officeClerk, phlProf, pilates, poet, president, preTeacher, psychologist, psyProf, pt, rapper, realestate, schoolCounselor, secretary, socialwork, speechpath, teachingAssistant, techConsul, therapist, traincond, unemployed, wallTiler, weightlifter, Yoga)
#change names to the word 
names(freq)[1] <- "accProf"
names(freq)[2] <- "adminassi"
names(freq)[3] <- "aircaptain"
names(freq)[4] <- "architect"
names(freq)[5] <- "armygeneral"
names(freq)[6] <- "babysitter"
names(freq)[7] <- "Basketball"
names(freq)[8] <- "burgerKing"
names(freq)[9] <- "busDriver"
names(freq)[10] <- "Business"
names(freq)[11] <- "cafeteria"
names(freq)[12] <- "cardiologist"
names(freq)[13] <- "carpenter"
names(freq)[14] <- "CEO"
names(freq)[15] <- "chemEng"
names(freq)[16] <- "childPsychologist"
names(freq)[17] <- "civilEng"
names(freq)[18] <- "collegedrop"
names(freq)[19] <- "congressm"
names(freq)[20] <- "constructionWorker"
names(freq)[21] <- "counselor"
names(freq)[22] <- "creative"
names(freq)[23] <- "criminal"
names(freq)[24] <- "cs"
names(freq)[25] <- "dataanalyst"
names(freq)[26] <- "electrician"
names(freq)[27] <- "elemteacher"
names(freq)[28] <- "Engineer"
names(freq)[29] <- "englishProf"
names(freq)[30] <- "executive"
names(freq)[31] <- "factoryWorker"
names(freq)[32] <- "fashion"
names(freq)[33] <- "firefighter"
names(freq)[34] <- "flightAttendant"
names(freq)[35] <- "florist"
names(freq)[36] <- "forkliftDriver"
names(freq)[37] <- "hairdresser"
names(freq)[38] <- "highdrop"
names(freq)[39] <- "hiphop"
names(freq)[40] <- "housecleaner"
names(freq)[41] <- "housekeeper"
names(freq)[42] <- "industrialEng"
names(freq)[43] <- "Janitor"
names(freq)[44] <- "jazzMus"
names(freq)[45] <- "landscaper"
names(freq)[46] <- "lawClerk"
names(freq)[47] <- "lawyer"
names(freq)[48] <- "librarian"
names(freq)[49] <- "mainWorker"
names(freq)[50] <- "mathProf"
names(freq)[51] <- "Mcdo"
names(freq)[52] <- "midwife"
names(freq)[53] <- "mua"
names(freq)[54] <- "nailtech"
names(freq)[55] <- "neurologist"
names(freq)[56] <- "neurosurgeon"
names(freq)[57] <- "nurse"
names(freq)[58] <- "officeClerk"
names(freq)[59] <- "phlProf"
names(freq)[60] <- "poet"
names(freq)[61] <- "president"
names(freq)[62] <- "preTeacher"
names(freq)[63] <- "psychologist"
names(freq)[64] <- "psyProf"
names(freq)[65] <- "pt"
names(freq)[66] <- "rapper"
names(freq)[67] <- "realestate"
names(freq)[68] <- "schoolCounselor"
names(freq)[69] <- "secretary"
names(freq)[70] <- "socialwork"
names(freq)[71] <- "speechpath"
names(freq)[72] <- "teachingAssistant"
names(freq)[73] <- "techConsul"
names(freq)[74] <- "therapist"
names(freq)[75] <- "traincond"
names(freq)[76] <- "unemployed"
names(freq)[77] <- "wallTiler"
names(freq)[78] <- "weightlifter"
names(freq)[79] <- "Yoga"
View(freq)
```

```{r put word with log(avg freq) in a data frame}
freqdataframe<-as.data.frame(freq)
#summary(freq)
```

```{r}
finalDataFrame<-rbind(freqdataframe, freqdataframe02)
summary(finalDataFrame)
mean<- -12.182
```

```{r conduct t test to see if there is a significant difference in word frequency in stimuli }
t.test(finalDataFrame$freq, mu = mean )

```
p value of the t-test is not less than 0.05 so this suggests that there is no significant difference in the word frequency in my stimuli 



